SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-25 docs/questioning.tex
minor addition on Section 1, Section 2 draft ready

Such attacks include Cross-Site Scripting ({\sc xss})
attacks~\cite{SG07}, {\sc sql} injection attacks~\cite{RL12b},
Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}, and
others. Attacks like these have been topping the vulnerability lists
of numerous bulletin providers like the Open Web Application Security
Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
({\sc owasp}) and {\sc
  mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
years. Consider the case of {\sc owasp}'s Top Ten project whose main
goal is to raise awareness about web application security by
identifying some of the most critical risks facing organizations which
is referenced by numerous researchers. In its three consecutive Top
Ten lists (2007, 2010, 2013), different executable source code-driven
injection attacks dominate the top five positions. Malicious users
find new ways to bypass defense mechanisms by using a variety of
techniques despite the numerous countermeasures that are being
introduced. Note that the number of systems developed to counter {\sc
  sql} injection attacks until 2006 was more than twenty~\cite{HVO06}.
Since then the number has doubled. In our research we focus on the top
{\sc tba} systems that counter application attacks, in terms of
citations.
% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.

@@

Application attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
{\sc xml} play an significant role in the development of either web or
mobile applications. For example, many applications have interfaces
where a user enters input to interact with the application's data,
thereby interacting with the underlying Relational Database Management
System ({\sc rdbms}). This input can become part of an {\sc sql} query
and executed on the target {\sc rdbms}. A code injection attack that
exploits the vulnerabilities of these interfaces by taking advantage
of input validation issues like incorrectly passed parameters or
incorrect type handling, is called an {\sc sql} injection
attack~\cite{CERT02,MS09,HVO06,SW06}. By using similar techniques
malicious users can perform other exploits based on {\sc dsl}s, like
{\sc xp}ath~\cite{SW06,CDL07,MKS09} and {\sc xml}~\cite{MSM13}. With
this kind of attacks, a malicious user can view sensitive information,
destroy or modify protected data, or even crash the entire
application.

A recent class of {\sc cia}s involve dynamic languages like Python,
Perl, JavaScript, and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
injection attacks, in particular, make up a large subset of dynamic
language-driven attacks. Such attacks are manifested when a web
application accepts and redisplays data of uncertain origin without
appropriate validation and filtering. Based on this flaw, an attacker
can manage to inject a script in the JavaScript engine of a browser
and alter its execution flow~\cite{ELX07}. JavaScript injection
attacks are considered as a critical issue in web application security
mainly because they are associated with major vulnerabilities such as:
{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{LZRL09} and
Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.

>>>>

Such attacks include Cross-Site Scripting ({\sc xss})
attacks~\cite{SG07}, {\sc sql} injection attacks~\cite{RL12b},
Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}, and
others. Attacks like these have been topping the vulnerability lists
of numerous bulletin providers like the Open Web Application Security
Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
({\sc owasp}) and {\sc
  mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
years. Consider the case of {\sc owasp}'s Top Ten project whose main
goal is to raise awareness about web application security by
identifying some of the most critical risks facing organizations which
is referenced by numerous researchers. In its three consecutive Top
Ten lists (2007, 2010, 2013), different executable source code-driven
injection attacks dominate the top five positions. Malicious users
find new ways to bypass defense mechanisms by using a variety of
techniques despite the numerous countermeasures that are being
introduced. Note that the number of systems developed to counter
{\sc sql} injection attacks until 2006 was more than twenty~\cite{HVO06}.
Since then the number has doubled.
Researchers have also indicated that the number of such attacks
is steadily increasing in recent years~\cite{SSL12}.

In our research we focus on the top
{\sc tba} systems that counter application attacks, in terms of
citations.
% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.

@@

Application attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
{\sc xml} play an significant role in the development of either web or
mobile applications. For example, many applications have interfaces
where a user enters input to interact with the application's data,
thereby interacting with the underlying Relational Database Management
System ({\sc rdbms}). This input can become part of an {\sc sql} query
and executed on the target {\sc rdbms}. A code injection attack that
exploits the vulnerabilities of these interfaces by taking advantage
of input validation issues like incorrectly passed parameters or
incorrect type handling, is called an {\sc sql} injection
attack~\cite{CERT02,MS09,HVO06,SW06}. By using similar techniques
malicious users can perform other exploits based on {\sc dsl}s, like
{\sc xp}ath~\cite{SW06,CDL07,MKS09} and {\sc xml}~\cite{MSM13}. With
this kind of attacks, a malicious user can view sensitive information,
destroy or modify protected data, or even crash the entire
application. {\sc html} is another {\sc dsl} that can be used
for malicious purposes when an application does not properly
handle user supplied data. Based on this vulnerability
an attacker can supply valid {\sc html},
typically via a parameter value, and inject their own
content into the page. {\sc html} injection is mainly associated
with {\sc xss} defects.

A recent class of {\sc cia}s involve dynamic languages like
JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
injection attacks, in particular, make up a large subset of dynamic
language-driven attacks. Such attacks are manifested when a web
application accepts and redisplays data of uncertain origin without
appropriate validation and filtering. Based on this flaw, an attacker
can manage to inject a script in the JavaScript engine of a browser
and alter its execution flow~\cite{ELX07}. JavaScript injection
attacks are considered as a critical issue in web application security
mainly because they are associated with major vulnerabilities such as:
{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{LZRL09} and
Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
In many cases {\sc xss} attacks involve the injection of
both {\sc html} and JavaScript code.
